Quantum Hoare Types

### 2019-10-30 paper/paper.tex
Even more cleanup

\documentclass[acmsmall,nonacm]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\acmJournal{PACMPL}
\acmVolume{}
\acmNumber{} %
\acmArticle{}
\acmYear{}
\acmMonth{}
\acmDOI{} %
\startPage{1}

\setcopyright{none}

@@

\title[Quantum Hoare Types]{Quantum Hoare Types}         %

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}

@@

Previous work such as Proto-Quipper\cite{ross2015algebraic} and \qwire\cite{paykin2018,rand2018a} utilize a linear type system and dependent types to enforce a small subset of semantic properties in the quantum setting such as the no-cloning theorem and whether a unitary operator is of the right dimension. These advances in quantum type systems although helpful, still fall short in encoding and enforcing even more useful properties that one would like to be able to express for the purpose of verification. Inspired by the use of Hoare triples in the verification of imperative programs and building on the idea of Hoare Types in classical programming languages, we propose Quantum Hoare Types aimed at enabling both sound static type checking and formal verification of quantum programs.

>>>>

\documentclass[acmsmall,nonacm,review,timestamp]{acmart}

\acmJournal{PACMPL}

\authorsaddresses{}

@@

\title{Quantum Hoare Types}         %

@@

@@

Previous work such as Proto-Quipper\cite{ross2015algebraic} and \qwire\cite{paykin2018,rand2018a} utilize a linear type system and dependent types to enforce a small subset of semantic properties in the quantum setting such as the no-cloning theorem and whether a unitary operator is of the right dimension. These advances in quantum type systems although helpful, still fall short in encoding and enforcing even more useful properties that one would like to be able to express for the purpose of verification. Inspired by the use of Hoare triples in the verification of imperative programs and building on the idea of Hoare Types in classical programming languages\cite{nanevski2008}, we propose Quantum Hoare Types aimed at enabling both sound static type checking and formal verification of quantum programs.
